### 2021-09-28 paper/output/document/paper41.tex
added cites for KG and kitcheR

%
\begin{isabellebody}%
\setisabellecontext{paper{\isadigit{4}}{\isadigit{1}}}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Novel Formalization of the Categorical Imperative%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this section, I present a custom formalization of the categorical imperative, as inspired by 
the goals from the previous chapter.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Logical Background%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
The previous attempts to model the categorical imperative in Chapter 2 partially failed due to 
lack of expressivity about the complexity of a maxim. Specifically, they treated actions as a single, 
monolithic unit of evaluation, whereas most Kantians consider the unit of evaluation for the FUL to the more
complex notion of a maxim. In this section, I will present some logical background necessarily to more fully 
capture the spirit of a maxim. I will begin by borrowing some machinery to handle ``subjects" who perform 
actions from Chapter 2.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{typedecl}\isamarkupfalse%
\ s\ %
\isamarkupcmt{s is the type for a ``subject," i.e. the subject of a sentence%
}\isanewline
\isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
\ os\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}s\ {\isasymRightarrow}\ t{\isacharparenright}{\isachardoublequoteclose}\ %
\isamarkupcmt{Recall that an open sentence maps a subject to a term to model substitution.%
}\isanewline
\isanewline
\isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
\ maxim\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}t\ {\isacharasterisk}\ os\ {\isacharasterisk}\ t{\isacharparenright}{\isachardoublequoteclose}\ %
\isamarkupcmt{Korsgaard interprets Kant's idea of a maxim as being equivalent 
to Aristotle's notion of logos or principle, which is a circumstance, act, goal pair. Read logos (C, A, G)
as ``In circumstance C, I will do A in order to G." A circumstance is represented as a set of worlds 
$t$ where that circumstance holds. A goal is a term because it can be true or false at a world if it 
is realized. An act is an open sentence because, once we substitute an agent in, an act can be true or 
false at a world if it is actually performed by that subject.

Korsgaard interprets a maxim as being equivalent to a logos, and thus only being composed of the features
above. Kitcher argues that a maxim should also include the motivation. This additional component is read 
as ``In circumstance C, I will do A in order to G because of M." where M may be ``duty" or ``self-love."
This captures Kant's idea that an action derives its moral worth from being done for the sake of duty itself.
Given that, under the Kantian constituvist view, the categorical
imperative completely defines duty, Kitcher argues that the FUL would obligate maxims of the form 
``In circumstance C, I will do A in order to G because I would will that I and everyone else simultaneously
will do A in order to G in circumstance C." In other words, the affirmative result of the FUL becomes 
the motivation for a moral action.

>>>>

%
\begin{isabellebody}%
\setisabellecontext{paper{\isadigit{4}}{\isadigit{1}}}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Novel Formalization of the Categorical Imperative%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this section, I present a custom formalization of the categorical imperative, as inspired by 
the goals from the previous chapter.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Logical Background%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
The previous attempts to model the categorical imperative in Chapter 2 partially failed due to 
lack of expressivity about the complexity of a maxim. Specifically, they treated actions as a single, 
monolithic unit of evaluation, whereas most Kantians consider the unit of evaluation for the FUL to the more
complex notion of a maxim. In this section, I will present some logical background necessarily to more fully 
capture the spirit of a maxim. I will begin by borrowing some machinery to handle ``subjects" who perform 
actions from Chapter 2.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{typedecl}\isamarkupfalse%
\ s\ %
\isamarkupcmt{s is the type for a ``subject," i.e. the subject of a sentence%
}\isanewline
\isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
\ os\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}s\ {\isasymRightarrow}\ t{\isacharparenright}{\isachardoublequoteclose}\ %
\isamarkupcmt{Recall that an open sentence maps a subject to a term to model substitution.%
}\isanewline
\isanewline
\isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
\ maxim\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}t\ {\isacharasterisk}\ os\ {\isacharasterisk}\ t{\isacharparenright}{\isachardoublequoteclose}\ %
\isamarkupcmt{Korsgaard \cite{actingforareason} interprets Kant's idea of a maxim as being equivalent 
to Aristotle's notion of logos or principle (insert cite), which is a circumstance, act, goal pair. Read logos (C, A, G)
as ``In circumstance C, I will do A in order to G." A circumstance is represented as a set of worlds 
$t$ where that circumstance holds. A goal is a term because it can be true or false at a world if it 
is realized. An act is an open sentence because, once we substitute an agent in, an act can be true or 
false at a world if it is actually performed by that subject.

Korsgaard interprets a maxim as being equivalent to a logos, and thus only being composed of the features
above. Kitcher \cite{whatisamaxim} argues that a maxim should also include the motivation. This additional component is read 
as ``In circumstance C, I will do A in order to G because of M." where M may be ``duty" or ``self-love."
This captures Kant's idea that an action derives its moral worth from being done for the sake of duty itself.
Given that, under the Kantian constituvist view, the categorical
imperative completely defines duty, Kitcher argues that the FUL would obligate maxims of the form 
``In circumstance C, I will do A in order to G because I would will that I and everyone else simultaneously
will do A in order to G in circumstance C." In other words, the affirmative result of the FUL becomes 
the motivation for a moral action.
